|

### 2021-05-30 article/article.Rmd
add tables, need fixing

[^huzeyfe]: Research Associate, Contemporary Brazilian History Research and Documentation Center, School of Social Sciences, Fundação Getulio Vargas, <huzeyfealptekin@gmail.com>.

@@

\footnotesize
\begin{longtable}{>{\raggedright\arraybackslash}p{3.9cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{1.1cm}}
\caption{Papers included in the meta-analysis, ordered by year of appearance}\\
\toprule
\raggedright Author(s) & \centering Journal & \centering Country & \centering Dependent Variable & \centering Method & \centering Institutional Design & \centering Electoral System
\tabularnewline
\midrule
\endhead 
```{r papers, echo = FALSE, results = 'asis', cache = T}
build_nams <- function(x) {
  x_ <- unlist(strsplit(as.character(x), ' & ', fixed = T, useBytes = T))
  if(length(x_) == 1) return(x_)
  else {
    aux <- x_[1]
      for (i in 2:length(x_))
        if (i == length(x_)){
          aux <- paste(aux, ' \\& \\\\ ', x_[i], sep = '')
        } else {
          aux <- paste(aux, ',\\\\ ', x_[i], sep = '')
        }
  }
  return(paste('\\begin{tabular}[t]{@{}l@{}}', aux,'\\end{tabular}', 
                   sep = ''))
}
aux <- dat %>%
  select(authoryear, journalCode, locationISO, depvar2, method, instdesign, elecsys3, year) %>%
  unique() %>%
  arrange(year)
for (i in 1:dim(aux)[1]) {
  cat(paste(build_nams(aux$authoryear[i]), ' & ', aux$journalCode[i], ' & ',
      aux$locationISO[i], ' & ', aux$depvar2[i], ' & ', 
      aux$method[i], ' & ', aux$instdesign[i], ' & ', 
      aux$elecsys3[i], ' \\\\ [0.5ex]', sep = ''), '\n')
}
```
\bottomrule
\label{tab:papers}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\vspace{-0.5cm}
\footnotetext{\textbf{Journal:} Unpub$=$Unpublished, JPE$=$Journal of Political
Economy, EJPE$=$European Journal of Political Economy, PC$=$Public Choice,
JPubE$=$Journal of Public Economics, JPriE$=$Journal of Private Enterprise,
APSR$=$American Political Science Review, SEJ$=$Southern Economic Journal,
UAR$=$Urban Affairs Review, SCID$=$Studies in Comparative International
Development, SSQ$=$Social Science Quarterly, SPPQ$=$State Politics and Policy
Quarterly, CPS$=$Comparative Political Studies, RivPE$=$Rivista di Politica
Economica, E\&P$=$Economics and Politics, NTJ$=$National Tax Journal.}
\footnotetext{\textbf{Country:} Country codes follow the ISO 3166-1 alpha-3
international standard.} 
\footnotetext{\textbf{Dependent Variable:} ExpPC$=$Per capita expenditure,
logExpPC$=$Natural logarithm of per capita expenditure, PCTGDP$=$Expenditure as
a percentage of GDP.}
\footnotetext{\textbf{Method:} OLS$=$Ordinary least squares, IV$=$Instrumental
variables, Panel$=$Panel data/fixed effects, RDD$=$Regression discontinuity
design.}
\footnotetext{\textbf{Electoral System:} M$=$Majoritarian, NM$=$Non-majoritarian (mixed or proportional
representation).} 
\end{minipage} 
\end{longtable}
\normalsize

@@

\footnotesize
```{r descriptive, warning=F, message=F, echo = FALSE, cache=TRUE, results='asis'}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Other coefficients", "Main sample")
aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
              year, published, instdesign) %>%
  rename(`Independent Variables` = indepvar2,
         `Year`                  = year,
         `Published work`        = published,
         `Estimation method`     = method,
         `Institutional Design`  = instdesign,
         `Electoral system`      = elecsys2)

@@

\vspace{0.5cm}
[TABLE GOES HERE]
\vspace{0.5cm}

>>>>

[^huzeyfe]: Independent Researcher, <huzeyfealptekin@gmail.com>.

@@

\footnotesize
\begin{longtable}{>{\raggedright\arraybackslash}p{3.9cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{1.1cm}}
\caption{Papers included in the meta-analysis, ordered by year of appearance}\\
\toprule
\raggedright Author(s) & \centering Journal & \centering Country & \centering Dependent Variable & \centering Method & \centering Institutional Design & \centering Electoral System
\tabularnewline
\midrule
\endhead 
```{r papers, echo = FALSE, results = 'asis', cache = T}
build_nams <- function(x) {
  x_ <- unlist(strsplit(as.character(x), ' & ', fixed = T, useBytes = T))
  if(length(x_) == 1) return(x_)
  else {
    aux <- x_[1]
      for (i in 2:length(x_))
        if (i == length(x_)){
          aux <- paste(aux, ' \\& \\\\ ', x_[i], sep = '')
        } else {
          aux <- paste(aux, ',\\\\ ', x_[i], sep = '')
        }
  }
  return(paste('\\begin{tabular}[t]{@{}l@{}}', aux,'\\end{tabular}', 
                   sep = ''))
}
aux <- dat %>%
  select(authoryear, journalCode, locationISO, depvar2, method, instdesign2, elecsys3, year) %>%
  unique() %>%
  arrange(year, depvar2)
aux2 <- aux %>%
  mutate(depvar2 = 'aux') %>%
  unique()
for(i in 1:dim(aux)[1]) {
  if(aux2$depvar2[aux2$authoryear == aux$authoryear[i]] == 'aux') {
    aux2$depvar2[aux2$authoryear == aux$authoryear[i]] = aux$depvar2[i]
  } else {
    aux2$depvar2[aux2$authoryear == aux$authoryear[i]] = paste(
      aux2$depvar2[aux2$authoryear == aux$authoryear[i]],
      aux$depvar2[i], sep = ', ')
  }
}
aux <- aux2
for (i in 1:dim(aux)[1]) {
  cat(paste(build_nams(aux$authoryear[i]), ' & ', aux$journalCode[i], ' & ',
      aux$locationISO[i], ' & ', aux$depvar2[i], ' & ', 
      aux$method[i], ' & ', aux$instdesign2[i], ' & ', 
      aux$elecsys3[i], ' \\\\ [0.5ex]', sep = ''), '\n')
}
```
\bottomrule
\label{tab:papers}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\vspace{-0.5cm}
\footnotetext{\textbf{Journal:} Unpub $=$ Unpublished, JPE $=$ Journal of Political
Economy, EJPE $=$ European Journal of Political Economy, PC $=$ Public Choice,
JPubE $=$ Journal of Public Economics, JPriE $=$ Journal of Private Enterprise,
APSR $=$ American Political Science Review, SEJ $=$ Southern Economic Journal,
UAR $=$ Urban Affairs Review, SCID $=$ Studies in Comparative International
Development, SSQ $=$ Social Science Quarterly, SPPQ $=$ State Politics and Policy
Quarterly, CPS $=$ Comparative Political Studies, RivPE $=$ Rivista di Politica
Economica, E\&P $=$ Economics and Politics, NTJ$=$National Tax Journal.}
\footnotetext{\textbf{Country:} Country codes follow the ISO 3166-1 alpha-3
international standard.} 
\footnotetext{\textbf{Dependent Variable:} ExpPC $=$ Per capita expenditure,
logExpPC $=$ Natural logarithm of per capita expenditure, PCTGDP $=$ Expenditure as
a percentage of GDP.}
\footnotetext{\textbf{Method:} OLS $=$ Ordinary least squares, IV $=$ Instrumental
variables, Panel $=$ Panel data/fixed effects, RDD $=$ Regression discontinuity
design.}
\footnotetext{\textbf{Electoral System:} M $=$ Majoritarian, NM $=$ Non-majoritarian (mixed or proportional
representation).} 
\end{minipage} 
\end{longtable}
\normalsize

@@

\footnotesize
```{r descriptive, warning=F, message=F, echo = FALSE, cache=TRUE, results='asis'}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Other coefficients", "Main sample")
aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
              year, published, instdesign2) %>%
  rename(`Independent Variables` = indepvar2,
         `Year`                  = year,
         `Published work`        = published,
         `Estimation method`     = method,
         `Institutional Design`  = instdesign2,
         `Electoral system`      = elecsys2)

@@

```{r, echo = FALSE, warning = FALSE, message = FALSE, results = 'hide', cache = TRUE}
res <- list()

# Aux fctns
strep <- function (x) {
  if(!is.na(x)) {
    return(ifelse(x<0.01, '***',ifelse(x<0.05,'**', ifelse(x<0.1,'*',''))))
  } else {
    return('')
  }
}

extract_coefs <- function(mod, modnam) {
  dfr <- data.frame(
     nams2 = row.names(mod[["beta"]]),
     est = mod[["beta"]],
     se = mod[["se"]],
     pval = mod[["pval"]],
     model = modnam
  )
  aux <- data.frame(nams = c("Intercept",
             "Indepvar: logN",
             "Indepvar: N",
             "Year",
             "Elecsys: Non-Majoritarian",
             "Published",
             "Method: Panel",
             "Method: IV",
             "Method: RDD",
             "Legislature: Unicameral"), 
             nams2 = c("intrcpt", 
                       "indepvar2logN", 
                       "indepvar2N", 
                       "year", 
                       "publishedYes", 
                       "elecsys2Non-Maj", 
                       "methodPANEL", 
                       "methodIV", 
                       "methodRDD",
                       "instdesign2Unicameral"))
  dfr <- left_join(aux, dfr) %>%
    mutate_if(is.numeric, list(~round(., digits = 4)))
  dfr$nams2 <- NULL
  return(dfr)
}

# Expenditure per capita - Restricted
mod <-  rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~indepvar2+year+published+elecsys2+method+instdesign2,
              test = "knha",
            subset = dat$depvar2=='ExpPC',
            slab = dat$authoryear,
            control=list(maxiter=1000))

res[[1]] <- extract_coefs(mod, "ExpPC")

# Expenditure per capita - Extended
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ ~indepvar2+year+published+elecsys2+method+instdesign2,
              test = "knha",
            subset = fulldat$depvar2=='ExpPC',
            slab = fulldat$authoryear)

res[[2]] <- extract_coefs(mod, "ExpPC - All coefs")

# Log of Expenditure per capita - Restricted
mod <- rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~indepvar2+year+published+elecsys2+method+instdesign2,
              test = "knha",
            subset = dat$depvar2=='logExpPC',
            slab = dat$authoryear)

res[[3]] <- extract_coefs(mod, "logExpPC")

# Log of Expenditure per capita - Extended
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ ~indepvar2+year+published+elecsys2+method+instdesign2,
              test = "knha",
            subset = fulldat$depvar2=='logExpPC',
            slab = fulldat$authoryear)

res[[4]] <- extract_coefs(mod, "logExpPC - All coefs")

## Expenditure as percentage GDP -- Restricted
mod <-  rma.mv(yi = coef,
              V = VAR,
              data = dat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method+instdesign2,
              test = "knha",
              sparse = TRUE,
              tdist = TRUE,
              subset = dat$depvar2=='PCTGDP',
              slab = dat$authoryear)

res[[5]] <- extract_coefs(mod, "PCTGDP")

## Expenditure as percentage GDP -- Extended
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~indepvar2+year+published+elecsys2+method+instdesign2,
              test = "knha",
            subset = fulldat$depvar2=='PCTGDP',
            slab = fulldat$authoryear)

res[[6]] <- extract_coefs(mod, "PCTGDP - All coefs")

mod <- rma.mv(yi = coef,
              V = VAR,
              data = dat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~depvar2+indepvar2+year+published+elecsys2+method+instdesign2,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
              slab = dat$authoryear)

res[[7]] <- extract_coefs(mod, "Full Model")

mod <- rma.mv(yi = coef,
              V = VAR,
              data = fulldat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~depvar2+indepvar2+year+published+elecsys2+method+instdesign2,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
              slab = fulldat$authoryear)

res[[8]] <- extract_coefs(mod, "Full Model - All coefs")
gcf <- function(mod, pos) {
  x <- mod$est[pos]
  y <- mod$pval[pos]
  if(!is.na(x)) {
    return(paste0(round(x, digits = 3), strep(y)))
  } else {
    return('')
  }
}
gcf2 <- function(mod, pos) {
  # round(res[[3]][2,3],3)`)`r strep(res[[3]][2,5])`
  x <- mod$se[pos]
  if(!is.na(x)) {
    return(paste0('(', round(x, digits = 3), ')'))
  } else {
    return('')
  }
}
```

\vspace{0.5cm}

```{=latex}
\begin{table}[htpb]
\caption{Meta Regression Results\label{tabregressions}}
\footnotesize
\centering
\begin{tabular}{lcccccccc}
\toprule
\midrule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Expenditure Per Capita} & \multicolumn{2}{c}{Log Expenditure Per Capita} & \multicolumn{2}{c}{Gov. Spending \% GDP} & \multicolumn{2}{c}{Full Model} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7} \cmidrule(l{3pt}r{3pt}){8-9}
& Restricted & Extended & Restricted & Extended & Restricted & Extended & Restricted & Extended \\
\midrule
Independent Variable: log($N$) & 
`r gcf(res[[1]], 2)` & `r gcf(res[[2]], 2)` & 
`r gcf(res[[3]], 2)` & `r gcf(res[[4]], 2)` & 
`r gcf(res[[5]], 2)` & `r gcf(res[[6]], 2)` &
`r gcf(res[[7]], 2)` & `r gcf(res[[8]], 2)` \\
& `r gcf2(res[[1]], 2)` & `r gcf2(res[[2]], 2)` & 
`r gcf2(res[[3]], 2)` & `r gcf2(res[[4]], 2)` & 
`r gcf2(res[[5]], 2)` & `r gcf2(res[[6]], 2)` & 
`r gcf2(res[[7]], 2)` & `r gcf2(res[[8]], 2)` \\
%
Independent Variable: $N$ &
`r gcf(res[[1]], 3)` & `r gcf(res[[2]], 3)` & 
`r gcf(res[[3]], 3)` & `r gcf(res[[4]], 3)` & 
`r gcf(res[[5]], 3)` & `r gcf(res[[6]], 3)` &
`r gcf(res[[7]], 3)` & `r gcf(res[[8]], 3)` \\
& `r gcf2(res[[1]], 3)` & `r gcf2(res[[2]], 3)` & 
`r gcf2(res[[3]], 3)` & `r gcf2(res[[4]], 3)` & 
`r gcf2(res[[5]], 3)` & `r gcf2(res[[6]], 3)` & 
`r gcf2(res[[7]], 3)` & `r gcf2(res[[8]], 3)` \\
%
Year & 
`r gcf(res[[1]], 4)` & `r gcf(res[[2]], 4)` & 
`r gcf(res[[3]], 4)` & `r gcf(res[[4]], 4)` & 
`r gcf(res[[5]], 4)` & `r gcf(res[[6]], 4)` &
`r gcf(res[[7]], 4)` & `r gcf(res[[8]], 4)` \\
& `r gcf2(res[[1]], 4)` & `r gcf2(res[[2]], 4)` & 
`r gcf2(res[[3]], 4)` & `r gcf2(res[[4]], 4)` & 
`r gcf2(res[[5]], 4)` & `r gcf2(res[[6]], 4)` & 
`r gcf2(res[[7]], 4)` & `r gcf2(res[[8]], 4)` \\
%
Non-Majoritarian (PR \& Mixed) & 
`r gcf(res[[1]], 5)` & `r gcf(res[[2]], 5)` & 
`r gcf(res[[3]], 5)` & `r gcf(res[[4]], 5)` & 
`r gcf(res[[5]], 5)` & `r gcf(res[[6]], 5)` &
`r gcf(res[[7]], 5)` & `r gcf(res[[8]], 5)` \\
& `r gcf2(res[[1]], 5)` & `r gcf2(res[[2]], 5)` & 
`r gcf2(res[[3]], 5)` & `r gcf2(res[[4]], 5)` & 
`r gcf2(res[[5]], 5)` & `r gcf2(res[[6]], 5)` & 
`r gcf2(res[[7]], 5)` & `r gcf2(res[[8]], 5)` \\
%
Published: Yes & 
`r gcf(res[[1]], 6)` & `r gcf(res[[2]], 6)` & 
`r gcf(res[[3]], 6)` & `r gcf(res[[4]], 6)` & 
`r gcf(res[[5]], 6)` & `r gcf(res[[6]], 6)` &
`r gcf(res[[7]], 6)` & `r gcf(res[[8]], 6)` \\
& `r gcf2(res[[1]], 6)` & `r gcf2(res[[2]], 6)` & 
`r gcf2(res[[3]], 6)` & `r gcf2(res[[4]], 6)` & 
`r gcf2(res[[5]], 6)` & `r gcf2(res[[6]], 6)` & 
`r gcf2(res[[7]], 6)` & `r gcf2(res[[8]], 6)` \\
%
Method: Panel & 
`r gcf(res[[1]], 7)` & `r gcf(res[[2]], 7)` & 
`r gcf(res[[3]], 7)` & `r gcf(res[[4]], 7)` & 
`r gcf(res[[5]], 7)` & `r gcf(res[[6]], 7)` &
`r gcf(res[[7]], 7)` & `r gcf(res[[8]], 7)` \\
& `r gcf2(res[[1]], 7)` & `r gcf2(res[[2]], 7)` & 
`r gcf2(res[[3]], 7)` & `r gcf2(res[[4]], 7)` & 
`r gcf2(res[[5]], 7)` & `r gcf2(res[[6]], 7)` & 
`r gcf2(res[[7]], 7)` & `r gcf2(res[[8]], 7)` \\
%
Method: IV & 
`r gcf(res[[1]], 8)` & `r gcf(res[[2]], 8)` & 
`r gcf(res[[3]], 8)` & `r gcf(res[[4]], 8)` & 
`r gcf(res[[5]], 8)` & `r gcf(res[[6]], 8)` &
`r gcf(res[[7]], 8)` & `r gcf(res[[8]], 8)` \\
& `r gcf2(res[[1]], 8)` & `r gcf2(res[[2]], 8)` & 
`r gcf2(res[[3]], 8)` & `r gcf2(res[[4]], 8)` & 
`r gcf2(res[[5]], 8)` & `r gcf2(res[[6]], 8)` & 
`r gcf2(res[[7]], 8)` & `r gcf2(res[[8]], 8)` \\
%
Method: RDD &
`r gcf(res[[1]], 9)` & `r gcf(res[[2]], 9)` & 
`r gcf(res[[3]], 9)` & `r gcf(res[[4]], 9)` & 
`r gcf(res[[5]], 9)` & `r gcf(res[[6]], 9)` &
`r gcf(res[[7]], 9)` & `r gcf(res[[8]], 9)` \\
& `r gcf2(res[[1]], 9)` & `r gcf2(res[[2]], 9)` & 
`r gcf2(res[[3]], 9)` & `r gcf2(res[[4]], 9)` & 
`r gcf2(res[[5]], 9)` & `r gcf2(res[[6]], 9)` & 
`r gcf2(res[[7]], 9)` & `r gcf2(res[[8]], 9)` \\
% 
Inst.: Unicameral & 
`r gcf(res[[1]], 10)` & `r gcf(res[[2]], 10)` & 
`r gcf(res[[3]], 10)` & `r gcf(res[[4]], 10)` & 
`r gcf(res[[5]], 10)` & `r gcf(res[[6]], 10)` &
`r gcf(res[[7]], 10)` & `r gcf(res[[8]], 10)` \\
& `r gcf2(res[[1]], 10)` & `r gcf2(res[[2]], 10)` & 
`r gcf2(res[[3]], 10)` & `r gcf2(res[[4]], 10)` & 
`r gcf2(res[[5]], 10)` & `r gcf2(res[[6]], 10)` & 
`r gcf2(res[[7]], 10)` & `r gcf2(res[[8]], 10)` \\
% 
Intercept & 
`r gcf(res[[1]], 1)` & `r gcf(res[[2]], 1)` & 
`r gcf(res[[3]], 1)` & `r gcf(res[[4]], 1)` & 
`r gcf(res[[5]], 1)` & `r gcf(res[[6]], 1)` &
`r gcf(res[[7]], 1)` & `r gcf(res[[8]], 1)` \\
& `r gcf2(res[[1]], 1)` & `r gcf2(res[[2]], 1)` & 
`r gcf2(res[[3]], 1)` & `r gcf2(res[[4]], 1)` & 
`r gcf2(res[[5]], 1)` & `r gcf2(res[[6]], 1)` & 
`r gcf2(res[[7]], 1)` & `r gcf2(res[[8]], 1)` \\
\bottomrule
\end{tabular}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\footnotetext{\textbf{Note:} {The restricted and extended samples include `r length(dat$id)` and `r length(fulldat$id)` study coefficients, respectively. We report the results from the permutation tests. Reference categories: Independent Variable: Upper House Size; Published $= No$; Non-Majoritarian; Method $= OLS$, Legislative: $= Non-Unicameral$. Significance codes: *** $p < 0.01$; ** $p < 0.05$; * $p < 0.10$.}}
\end{minipage}
\end{table}
```

\vspace{0.5cm}
